%----------------------------------------------------------------------------
%----------------------------------------------------------------------------
%----------------------------------------------------------------------------
%----------------------------------------------------------------------------
The results of the numerical analysis of LIDAR geometries imply: high power sub nanosecond pulsed laser open the door to high sensitivity instruments; and sucessful low power ``benchtop'' experiments may be harder than large scale experiments if power is not a factor.

The three color LIF simulations suggest a high discrimination level between two very similar molecular species.

The numerical studies of the STIRAP process show many advantges to using this process in the multi-color LIF excitation process.

The comparaison between LIF data obtained from two differently prepared iodine sample cells show that the LIF process is fundementally robust.

The dye laser wavelenght scan LIF data sets show that commercial lasers are capabile of level discrimination in an evacuated iodine cell.

The single LIF line decay data shows that there may be many processes contributing to the non-radiative decay chanels in excited molecular iodine; however, even in a modestly prepared cell, the decay is long compared to the excitation time - this leaves the door open to multi-color experiemnts.

The measurements of the dye laser output transvers profile and this profile's stability show that the Sirah pulse dye lasers may make a three color experiment prohibitive.

The measurements of the dye laser output RF content imply the dye lasers mode content severly degrades the dye laser's capability to control molecular iodine.

The confocal etalon test show us that the confocal etalon will be useful as a beam analyizer but will make a poor filter because of its poor efficency.

%----------------------------------------------------------------------------
%----------------------------------------------------------------------------
