%----------------------------------------------------------------------------
%----------------------------------------------------------------------------
%\input{system/intro/intro.tex}
%----------------------------------------------------------------------------
%----------------------------------------------------------------------------
\section{General description}
Armed with the information from the previous chapters, we outline methods employed to condition the dye laser system for coherent control spectroscopy. This section introduces the systems used to condition a single dye laser, then outlines the method of mixing and delaying the pulses, and finally gives a brief description of the interaction region and the data acquisition chain.
%----------------------------------------------------------------------------
\subsection{Single dye laser conditioning}
\input{system/general/single_dye.tex}
%----------------------------------------------------------------------------
\subsection{Controlled three pulse sequence}
\input{system/general/three_pulse.tex}
%----------------------------------------------------------------------------
\subsection{Interaction and data acquisition}
\input{system/general/daq.tex}
%----------------------------------------------------------------------------
%----------------------------------------------------------------------------
\section{Layout}
The entire system will span three optical tables: the laser beams start on the ``dye laser'' table, proceed to a ``conditioning'' table, then finally reach an ``interaction'' table. This section gives the precise layout of the key optical components (here we assume a pinhole will be used for completeness).
%----------------------------------------------------------------------------
\subsection{Dye laser table}
\input{system/layout/dye_table.tex}
%----------------------------------------------------------------------------
\subsection{Beam conditioning table}
\input{system/layout/cond_table.tex}
%----------------------------------------------------------------------------
\subsection{Interaction table}
\input{system/layout/inter_table.tex}
%----------------------------------------------------------------------------
%----------------------------------------------------------------------------
\section{Filters}
There are three filters under consideration: a temporal shaper, a spatial filter, and a band pass spectral filter. The filter with the most development history is the temporal shaper: the Pockels cell. The pinhole is analyzed here in terms of its effectiveness as a spatial filter for high peak power pulsed control experiments. A fundamental limitation on the transmitted power of etalon type filters is parameterized -- this brings into question the rationale for using etalons when beam energy is important to the experiment. Finally we present the results of a test of a confocal etalon purchased for evaluation purposes.
%----------------------------------------------------------------------------
\subsection{Pockels cells DC test}
\input{system/filters/dc.tex}
%----------------------------------------------------------------------------
\subsection{Pockels cells minimum pulse length}
\input{system/filters/min_pulse.tex}
%----------------------------------------------------------------------------
\subsection{Pinholes}
\input{system/filters/beam_to_focus.tex}
\input{system/filters/pinhole.tex}
%----------------------------------------------------------------------------
\subsection{General discussion on etalon efficiency}
\input{system/filters/planaretalon.tex}
%----------------------------------------------------------------------------
\subsection{Confocal etalon test}
%----------------------------------------------------------------------------
\input{system/confocal/data.tex}
%----------------------------------------------------------------------------
%----------------------------------------------------------------------------
%----------------------------------------------------------------------------
%----------------------------------------------------------------------------
%----------------------------------------------------------------------------
