\documentstyle[hyperref, margin, line]{res}
\hypersetup{backref, pdfpagemode=FullScreen, colorlinks=true,backref}
\def\Cplusplus{{\rm C\raise.5ex\hbox{\small ++}}}
% 'st' 'nd' 'rd' 'th' superscripts for numbers
\def\first{{\raise.5ex\hbox{\small st}}}
\def\second{{\raise.5ex\hbox{\small nd}}}
\def\third{{\raise.5ex\hbox{\small rd}}}
\def\fourth{{\raise.5ex\hbox{\small th}}}

%use most of page
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\voffset}{-0.5in}
%\addtolength{\textwidth}{1.25in}
%\addtolength{\textheight}{1in}

%use only a bit more page than default
\addtolength{\oddsidemargin}{-0.30in}
\addtolength{\voffset}{-0.50in}
%was -.30
\addtolength{\textwidth}{0.90in}
\addtolength{\textheight}{1.50in}
%was .60

%my name format
\renewcommand{\namefont}{\LARGE\emph}

\begin{document}
\name{Daniel P. Lamblin}
\address{
  329 East 94\fourth{} St. Apt. 12,
  New York NY 10128
}

\address{
  \texttt{daniell at slithy.toves.net}\\
  \small{
  \href{http://www.syntaxerr.org/~daniell/resume/}{http://www.syntaxerr.org/$\sim$daniell/resume/}
  }
}

\begin{resume}

\section{\textsc{Objective}}
A full-time software development position.\\If you received this r\'esum\'e, it would contain a more job-specific objective or cover letter than this web-r\'esum\'e.  I do contract and internship-style work in addition to my regular job on occasion.  I would be interested in hearing from you if you found my abilities to be a potential fit.

\section{\textsc{Experience}}
\begin{format}
  \employer{l}\title{r}\\
  \location{l}\dates{r}\\
  \body\\
\end{format}

\employer{\textbf{Richmond Research}}
\title{\emph{Programmer}}
\location{New York, NY.}
\dates{\textbf{February 2003 -- Present}}
\begin{position}
Streamlined report generation and developed web based services
using Perl, PHP, Visual Basic and Flash MX.
\end{position}

\employer{\textbf{Mile New York}}
\title{\emph{Website Programmer}}
\location{Fort Lee, NJ.}
\dates{\textbf{October 2002 -- November 2003}}
\begin{position}
Established the backend Perl, CGIs, and MySQL database for MileNY's e-commerce site.
\\
{\small{See \href{http://www.milenewyork.com/}{http://www.milenewyork.com/}.}}
\end{position}

\employer{\textbf{EMC Corporation}}
\title{\emph{Associate Software Engineer}}
\location{Milford, MA.}
\dates{\textbf{June 2000 -- October 2001}}
\begin{position}
Maintained code-base by tracking defects and feature requests.
Coordinated with team members and other groups for defect reproduction, analysis and patch testing.
Made extensive use of C with RPC, threading, signals, and version control software.
\end{position}

\employer{\textbf{Worcester Area Student ACM Chapter}}
\title{\emph{Web Master}}
\location{Worcester, MA.}
\dates{\textbf{Aug. 1998 -- Aug. 1999}}
\begin{position}
Maintained and configured Apache based web server.
\\
Conceived and designed web site to be organized, and maintainable.
\\
{\small{See \href{http://www.acm.wpi.edu/}{http://www.acm.wpi.edu/}.}}
\end{position}


\section{\textsc{Education}}
\emph{Bachelor of Science in Computer Science}, May 1999.\\
Worcester Polytechnic Institute, Worcester, MA.

\emph{Courses}: Introduction to Machine Learning; Video Game Design \& Technology. [2003]\\
Columbia University, New York, NY.

\section{\textsc{Qualifications}}
\emph{Training}: Sun course for Sys V Inter-Process Communication and Threading [2000]

\emph{Programming Languages}: C, \Cplusplus, Java, LISP, 80x86 and 68k Assembly, Visual Basic, VHDL

\emph{Tools}: Perl, Unix Shell Scripts (sh, bash), PHP, clearcase, dbx

\emph{Operating Systems}: Solaris, MacOS X, Linux, [Open/Net]BSD, Windows NT

\emph{Language Skills}:
Spoken and written English; spoken Swiss German and some French

\section{\textsc{Activities}}
Configure, maintain, and administer NetBSD and Linux servers for email, network storage, web, and sftp services.\\
December 1999 -- Current

Consulted for the design, construction, programming and testing
of the embedded component
of a physical computing installation project with an artist 
at Parsons School of Design.\\
January  2002 -- May 2002

Refined a \LaTeX{} based system of formatting and editing r\'esum\'es
across four common formats through Makefiles and scripts.
{\small{See \href{http://www.syntaxerr.org/~daniell/resume/}{http://www.syntaxerr.org/$\sim$daniell/resume/}}}\\
October 2001 -- November 2001 (some revisions made later)


\end{resume}
\end{document}
