%----------------------------------------------------------------------------
%------------------------------Broad objectives------------------------------
%----------------------------------------------------------------------------
This chapter chronicles the stages of laboratory development undergone over the past few years. The main measurements at each stage were used as a guide to develop the equipment and techniques required for demonstration of molecular control in LIDAR systems.
%----------------------------------------------------------------------------
%----------------------------------So what?----------------------------------
%----------------------------------------------------------------------------

As each stage was completed various components of the apparatus were either designed and assembled or evolved to the next generation. After the installation of the PMT at its output the monochromator served each experiment well until the recent aromatic compound measurements. The Hg pulser and Pockles cell system went through various stages of development starting with the initial tests of the Hg pulser on LED's to the integration of the system with the YAG pumped dye laser system during the fluorescence line decay measurements. The software model was tested at each stage from the familiar non-resonant HeNe LIF to pulsed resonant dye LIF. The data acquisition system was built for the first dye laser experiments and has remained relatively unchanged since then. Recently, a calibration issue with the monochromator self scan feature has prompted the need of a second generation of the data acquisition software.
%----------------------------------------------------------------------------
%---------------------------------Synthesize---------------------------------
%----------------------------------------------------------------------------
%----------------------------------------------------------------------------
%----------------------------------------------------------------------------
%----------------------------------------------------------------------------
